---
title: "Hackathon Data Analysis"
output: html_notebook
---

Add libraries, import and save files.

```{r}
library(tidyverse)
library(ggplot2)

setwd('/Users/jameswelch/Dropbox (Personal)/NYDSA/Work/Hackathons/NYCDSA_Hackathon_Oct_2020/James')

churn_trunc <- read_csv("./trunc_churn.csv")
members_trunc <- read_csv("./trunc_members.csv")
transaction_trunc <- read_csv("./trunc_transaction.csv")
users_trunc <- read_csv("./trunc_users.csv")
```

Wrange that data
-convert numeric dates to actual date types

```{r, resutls = 'hide'}
# members_trunc <- members_trunc %>% 
#   mutate(.,registration_init_time = as.Date(as.character(registration_init_time),"%Y%m%d"))
# transaction_trunc <- transaction_trunc %>%  
#  mutate(.,transaction_date = as.Date(as.character(transaction_date),"%Y%m%d"))
#transaction_trunc <- transaction_trunc %>%  
#  mutate(.,membership_expire_date = as.Date(as.character(membership_expire_date), format = "%Y %m %d"))
users_trunc <- users_trunc %>%  
  mutate(.,date = as.Date(as.character(date),format = "%Y%m%d"))
```

Churn dataframe for QC
```{r}
print("Churn Dataframe")
print(paste0("total entires: ", length(churn_trunc$is_churn)))
print(paste0("number unique msno: ",length(unique(churn_trunc$msno))))
print(paste0("total churns: ", sum(churn_trunc$is_churn)))
print(paste0("percentage churns: ", sum(churn_trunc$is_churn)/length(churn_trunc$is_churn)*100, "%"))

```
Members dataframe for QC
```{r}
print("Members_trunc")
print(paste0("total entires: ", length(members_trunc$msno)))
print(paste0("number unique msno: ",length(unique(members_trunc$msno))))
print(paste0("number of cities: ", length((unique(members_trunc$city)))))
print(paste0("pop range in each city: ", members_trunc %>% group_by(., city) %>% count() %>%  range() ))
print(paste0("City 1 is probably a null when entering the form, or the first city the company started in."))
members_trunc %>% group_by(., city) %>% count()
print("see grouped_df for by city counts")
hist(members_trunc$city)
print("see histograme for by city counts")
print("see df and histogram for bd")
group_by(members_trunc, as.factor(members_trunc$bd)) %>% count()
hist(members_trunc$bd)
hist(members_trunc[which(members_trunc$bd>=5 & members_trunc$bd<100),]$bd)

print("obvious negaitve and extremely high (>100) can be ignored as truthful. ")
print("age=0 is roughly the same count as city, same member ids?")
print(paste0("gender breakdown(Female/male/NA: ",group_by(members_trunc,gender) %>% count())[2])
print("see datagrame of registration types")
members_trunc %>% group_by(., registered_via) %>% count()
print(paste0("Registration start data range",range(members_trunc$registration_init_time)))

```

Explore usage dataset
assemble dataframe with churn added
```{r}
users_seg <- merge(users_trunc,churn_trunc, by='msno', all = TRUE)
```
Missingness
```{r}
sum(is.na(users_seg$date))
#head(users_seg,20)

colSums(is.na(users_seg))

users_seg[is.na(users_seg$date),]
sum(users_seg[is.na(users_seg$date),]$is_churn)
print("percentage churn: ")
(sum(users_seg[is.na(users_seg$date),]$is_churn) / length(users_seg[is.na(users_seg$date),]$is_churn)) * 100


users_seg <- users_seg %>%  filter(., date != is.na(date))

```
Seems to be a by-product of the join, there is msno for users without corresponding user data. Perhaps this is users who pay but don't use the product or some issue with the data collection? The rate of churn seems to be roughly the same (8.9% vs 9.2% overall). These entries with missing data are dropped for this analysis. 


Maybe there is a clear pattern in usage? The log scale was chosen due to the wide spread in listening times.
```{r}
users_seg %>% 
  filter(., total_secs != is.na(total_secs)) %>% 
  mutate(., is_churn = as.factor(is_churn), .keep = c("all")) %>%
  mutate(., total_min = total_secs/60) %>% 
  ggplot(., aes(x = is_churn, y = log(total_min))) +
  geom_boxplot()

users_seg %>% 
  filter(., total_secs != is.na(total_secs)) %>% 
  mutate(., is_churn = as.factor(is_churn), .keep = c("all")) %>%
  mutate(., total_min = total_secs/60) %>% 
  ggplot(., aes(x = is_churn, y = (total_min))) +
  geom_boxplot()

#users_seg %>% 
  # filter(., total_secs != is.na(total_secs)) %>% 
  # mutate(., is_churn = as.factor(is_churn), .keep = c("all")) %>%
  # mutate(., total_min = total_secs/60) %>% 
  # ggplot(., aes(x = is_churn, y = log(total_min))) +
  # geom_violin()
```
Visually, they look identical. There are some weird outliers, 2000 minutes of songs per day? Maybe the date feature is when the user started a session in rather than the strict date of play?

Statistically 
```{r}
user_seg_ttest <- users_seg %>% 
  mutate(., is_churn = as.factor(is_churn), .keep = c("all"))

  t.test(user_seg_ttest$total_secs[user_seg_ttest$is_churn == 0], y = user_seg_ttest$total_secs[user_seg_ttest$is_churn == 1], var.equal = F)
  var.test(user_seg_ttest$total_secs[user_seg_ttest$is_churn == 0], y = user_seg_ttest$total_secs[user_seg_ttest$is_churn == 1])
  
  print("Not Churn Mean")
  mean(user_seg_ttest$total_secs[user_seg_ttest$is_churn == 0])
  print("Churn Mean")
  mean(user_seg_ttest$total_secs[user_seg_ttest$is_churn == 1])
  print("difference in means:")
  mean(user_seg_ttest$total_secs[user_seg_ttest$is_churn == 0]) - mean(user_seg_ttest$total_secs[user_seg_ttest$is_churn == 1])
  print("or in minutes: ")
    (mean(user_seg_ttest$total_secs[user_seg_ttest$is_churn == 0]) - mean(user_seg_ttest$total_secs[user_seg_ttest$is_churn == 1])) / 60
```
This also appear indistingusihable. Perhaps the pattern of usage, rather than the total will better characterize those who leave? Varience is unequal between the groups higher in the non-churn group.


How much data do we have for each user?
```{r}
msno_days <- users_seg %>% 
  group_by(., msno) %>% 
  count(., msno, is_churn)

#unique users / quick QC
#without date grouping = 15457
# with date grouping = 277101, which is equivalent to our inital set
print("number of unique msno in users_truncated")
length(unique(users_seg$msno))
print("number of msno when counting dates")
length(msno_days$msno)

msno_days %>% 
  ggplot(., aes(x = n,)) +
  geom_histogram(bins = 31) 

msno_days %>% 
  ggplot(., aes(x = n)) +
  geom_density()


```

Exploring number of days the product is used might be a fruitful avenue as an independent analysis.
Why is 15 such a common amount compared to 14 or 16? Perhaps we are catching people signing up in the middle of the data capture? 
```{r}
msno_days %>% 
  ggplot(., aes(x = as.factor(is_churn), y = n)) +
  geom_boxplot() +
  ylab("Number of days of observations per msno")
```
Again, there seems to be a slight difference between, perhaps the shape is different?


```{r}
msno_days %>% 
  ggplot(., aes(x = n, group = as.factor(is_churn), fill = as.factor(is_churn))) +
  geom_density(alpha = 0.4, position = "fill")
```


How do we characterize a day or activity?
- engagement (number of interventions in playing)
- choosiness (number of interventions before 75 or 98%)
-percentage completed
-average song length (feels weak)
-date played?
How do we characterize multiple days?
How do we characterize a user?

Ideas
- how does user behavior and likelihood to stay interact?
- high intervention versus low intervention in song choice
- city by city usage patterns?
- are payment methods more likely to churn than others?
- how are the people that leave?
--what does usage look like?
--what payment plans, information?


Price per day of plan:
```{r}

hist(transaction_trunc$plan_list_price / transaction_trunc$payment_plan_days)
filter(transaction_trunc, 1> transaction_trunc$plan_list_price / transaction_trunc$payment_plan_days)
```
Almost everyone pays the same price per day of service.

Seconds per month by user
```{r}
#length(unique(users_seg$msno)) 15457 if 20k drop NA



user_activity <- users_seg %>% 
  group_by(., msno) %>% 
  summarise(., num_active_days = length(unique(date)), num_seconds = sum(total_secs), is_churn = as.factor(mean(is_churn)))

length(unique(user_activity$msno))

user_activity %>% 
  ggplot(., aes(x = num_active_days, y = num_seconds)) +
  geom_point(aes(shape = is_churn,color=is_churn,))

# user_activity %>% 
#   ggplot(., aes(x = is_churn, y = num_seconds)) +
#   geom_boxplot()
# 
# user_activity %>% 
#   ggplot(., aes(x = is_churn, y = num_active_days)) +
#   geom_boxplot()

user_activity %>%
  ggplot(., aes(x = is_churn, y = num_seconds /num_active_days)) +
  geom_boxplot()

```
Not much visually different, churners seem to blend in with regular users


Subscription length
```{r}
churn_trunc <- read_csv("./trunc_churn.csv")
members_trunc <- read_csv("./trunc_members.csv")
transaction_trunc <- read_csv("./trunc_transaction.csv")

members_trunc <- members_trunc %>%
  mutate(.,registration_init_time = as.Date(as.character(registration_init_time),"%Y%m%d"))
transaction_trunc <- transaction_trunc %>%
 mutate(.,transaction_date = as.Date(as.character(transaction_date),"%Y%m%d"))
transaction_trunc <- transaction_trunc %>%
 mutate(.,membership_expire_date = as.Date(as.character(membership_expire_date), format = "%Y %m %d"))

T_and_M <- merge(transaction_trunc, members_trunc, by='msno', all= TRUE)

T_and_M <- T_and_M %>% filter(.,registration_init_time != is.na(registration_init_time)) %>% 
              filter(., transaction_date != is.na(transaction_date))

T_and_M <- T_and_M %>% mutate(., registraiton_length = abs(as.integer(difftime(registration_init_time, transaction_date, units='days'))))
T_and_M <-merge(T_and_M, churn_trunc, by='msno', all=TRUE)

T_and_M %>% 
  ggplot(., aes(x=registraiton_length, group= as.factor(is_churn), fill = as.factor(is_churn))) +
  geom_histogram(position = "stack")
T_and_M %>% 
  ggplot(., aes(x=registraiton_length, group= as.factor(is_churn), fill = as.factor(is_churn))) +
  geom_histogram(position = "fill")


hist(T_and_M$registraiton_length, na.rm = T)


T_and_M <- T_and_M %>% 
  mutate(., rev_per_day = plan_list_price / payment_plan_days)

T_and_M %>% 
  ggplot(., aes(x=registraiton_length, y = rev_per_day, group = as.factor(is_churn), color = as.factor(is_churn))) +
  geom_point()

T_and_M %>% 
  ggplot(., aes(x=registraiton_length, y = plan_list_price, group = as.factor(is_churn), color = as.factor(is_churn))) +
  geom_point()

T_and_M %>% 
  ggplot(., aes(x=registraiton_length, y = payment_plan_days, group = as.factor(is_churn), color = as.factor(is_churn))) +
  geom_point()

T_and_M %>% 
  ggplot(., aes(x= as.factor(is_churn), y=log(plan_list_price))) +
  geom_boxplot()

T_and_M %>% 
  group_by(., payment_plan_days, plan_list_price, is_churn) %>%  #payment plan days, list price, churn
  summarise(., number_users = n()) %>% 
  mutate(., )
  pivot_wider(., names_from = is_churn, values_from = number_users, values_fill = 0) %>% 
  mutate(., unq_ID = paste(payment_plan_days, plan_list_price, sep = "_"),
            #'0' = stayed,
            #'1' = left,
            #total_user = sum(stayed, left),
            #percent_stay = stayed / total_user,
            #percent_left = left / total_user
         )


T_and_M %>% 
  group_by(., payment_plan_days, plan_list_price, is_churn) %>%  #payment plan days, list price, churn
  summarise(., number_users = n()) %>% 
  mutate(., unq_ID = as.character(paste(payment_plan_days, plan_list_price, sep = "_"))) %>% 
  #           0 = stayed,
  #           1 = left,
  #           total_user = sum(stayed, left)) %>% 
  ggplot(., aes(x=unq_ID, y = number_users, group = is_churn,fill = is_churn)) +
    geom_bar(stat = "identity", position  = "stack" ) #fill

T_and_M %>% 
  group_by(., payment_plan_days, plan_list_price, is_churn) %>%  #payment plan days, list price, churn
  summarise(., number_users = n()) %>% 
  mutate(., unq_ID = as.character(paste(payment_plan_days, plan_list_price, sep = "_"))) %>% 
  #           0 = stayed,
  #           1 = left,
  #           total_user = sum(stayed, left)) %>% 
  ggplot(., aes(x=unq_ID, y = number_users, group = is_churn,fill = is_churn)) +
    geom_bar(stat = "identity", position  = "fill" )


T_and_M %>% 
  group_by(., payment_plan_days, plan_list_price, is_churn) %>%  #payment plan days, list price, churn
  summarise(., number_users = n()) %>% 
  mutate(., unq_ID = as.character(paste(payment_plan_days, plan_list_price, sep = "_"))) %>% 
  #           0 = stayed,
  #           1 = left,
  #           total_user = sum(stayed, left)) %>% 
  ggplot(., aes(x=as.factor(payment_plan_days), y = number_users, group = is_churn,fill = is_churn)) +
    geom_bar(stat = "identity", position  = "fill" )

T_and_M %>% 
  group_by(., payment_plan_days, plan_list_price, is_churn, is_auto_renew) %>%  #payment plan days, list price, churn
  summarise(., number_users = n()) %>% 
  mutate(., unq_ID = as.character(paste(payment_plan_days, plan_list_price, sep = "_"))) %>% 
  #           0 = stayed,
  #           1 = left,
  #           total_user = sum(stayed, left)) %>% 
  ggplot(., aes(x=payment_plan_days, y = plan_list_price, group = is_churn,color = is_churn, )) +
    geom_point( aes(size = number_users, shape=as.factor(is_auto_renew))  )


#df %>% spread(key, value) is equivalent to df %>% pivot_wider(names_from = key, values_from = value)

# msno_days %>% 
#   ggplot(., aes(x = n, group = as.factor(is_churn), fill = as.factor(is_churn))) +
#  geom_density(alpha = 0.4, position = "fill")

T_and_M %>% 
  ggplot(., aes(x = as.factor(is_auto_renew)))



```
CHurn seems to be distributed evenly acorss length of subscription. 



Feature engineering:
These are some "listening session features" I came up with, the ones with proxy are to try and model variables in the literature.
Average time at skip = weighted average of columns using the center point of the categories. (Num_25 = 0.1, num_50 = 0.375, num_75 = 0.625, num_985 = 0.8675, num_100 = 1) <25% and 100 are weighted differently to "pull" in a direction.
Percent early skips = Num_25 + Num_50 / total skips
Engagement = total skips / time played
Range_proxy = unique songs / early skips
Search_proxy = early skips / time (lots of skips for the amount listened) (percentage early skips versus total skips?)
Tilt_proxy = total skips (same as engagement?)

unique listens?
total songs - 

skips per full song


```{r}

users_seg <- users_seg %>% 
  rowwise() %>% 
  mutate(., 
        total_skips = sum(num_25, num_50,num_75, num_985, num_100),
        avg_skip_time = (num_25*0.1 + num_50*0.375 + 
                           num_75*0.625 + num_985*0.8675 + 
                           num_100*1 )/ total_skips,
        early_skips = sum(c(num_25, num_50)),
        late_skips = sum(c(num_985, num_100)),
        percent_early_skips = early_skips / total_skips,
        skips_per_secs = total_skips / total_secs,
        range_proxy = ifelse(early_skips != 0, num_unq / early_skips, 4000),
        serach_proxy = early_skips / total_secs,
        tilt_proxy = total_skips, 
        #final version?
        plays_per_unique = total_skips / num_unq,
        skips_per_full = ifelse(late_skips != 0, early_skips/ late_skips, 150),
        outer_skips = sum(c(num_25,num_100))
        )

hist(users_seg$avg_skip_time)
range(users_seg$avg_skip_time)

hist(users_seg$total_skips)


users_seg %>% 
  filter(., avg_skip_time >0.9)

correl <- round(cor(select(users_seg, -c(msno,date))),1)

ggcorrplot(correl, hc.order = T,
           type = "lower",
           lab = T,
           lab_size = 2,
           method="circle",
           ggtheme = theme_bw)

```


Repeat but grouping by user before feature generation
```{r}
agg_users <- users_seg %>% 
  group_by(., msno) %>% 
  summarise(., days_played = n(), 
            num_25=sum(num_25), 
            num_50=sum(num_50), 
            num_75=sum(num_75), 
            num_985=sum(num_985), 
            num_100=sum(num_100),
            num_unq=sum(num_unq),
            total_secs=sum(total_secs),
            is_churn=mean(is_churn)
            )
length(unique(agg_users$msno)) #15457
```

```{r}
library(tidyverse)
library(ggplot2)

agg_users <- agg_users %>%  
 rowwise() %>% 
  mutate(., 
        total_skips = sum(num_25, num_50,num_75, num_985, num_100),
        avg_skip_time = (num_25*0.1 + num_50*0.375 + 
                           num_75*0.625 + num_985*0.8675 + 
                           num_100*1 )/ total_skips,
        early_skips = sum(c(num_25, num_50)),
        late_skips = sum(c(num_985, num_100)),
        percent_early_skips = early_skips / total_skips,
        skips_per_secs = total_skips / total_secs,
        range_proxy = ifelse(early_skips != 0, num_unq / early_skips, 4000),
        serach_proxy = early_skips / total_secs,
        tilt_proxy = total_skips, 
        #final version?
        plays_per_unique = total_skips / num_unq,
        skips_per_full = ifelse(late_skips != 0, early_skips/ late_skips, 150),
        outer_skips = sum(c(num_25,num_100))
        )

```
range proxy, 27k at most (unique / early skips) set to 3 or 4k. (no early skips) Most are low listeners or late skipers.

skips per full: highest value is 80 the rest are infinity. set to 150.




Data exploration
```{r}
hist(agg_users$avg_skip_time)

hist(agg_users$num_25 / agg_users$total_skips)
hist(agg_users$num_50 / agg_users$total_skips)
hist(agg_users$num_75 / agg_users$total_skips)
hist(agg_users$num_985 / agg_users$total_skips)
hist(agg_users$num_100 / agg_users$total_skips)
```

more complicated
```{r}
agg_users %>% 
  ggplot(., aes(x=avg_skip_time)) +
  geom_histogram()

agg_users %>% 
  ggplot(., aes(x=total_skips, group= as.factor(is_churn), fill = as.factor(is_churn))) +
  geom_histogram(position = "stack")

agg_users %>% 
  ggplot(., aes(x=total_skips, group= as.factor(is_churn), fill = as.factor(is_churn))) +
  geom_histogram(position = "fill")

#install.packages("ggcorrplot")
library(ggcorrplot)

correl_assembly <- agg_users %>% 
  select(., -c(msno))

correl <- round(cor(select(agg_users, -msno)),1)

ggcorrplot(correl, hc.order = T,
           type = "lower",
           lab = T,
           lab_size = 2,
           method="circle",
           ggtheme = theme_bw)


#averg search time versus search proxies:

plot_avgskip_vs_skipPerFull <- agg_users %>% 
  ggplot(., aes(x = avg_skip_time, y = skips_per_full, group = as.factor(is_churn))) +
  geom_point(aes(color = as.factor(is_churn)))

many_boxes <- agg_users %>% 
  ggplot(., aes(as.factor(is_churn), )) +
  geom_boxplot()

for (thingy in colnames(select(agg_users, -msno))){
  plot_name <-ggplot(agg_users, aes(as.factor(is_churn), y = agg_users$thingy)) +
    geom_boxplot()
  print(plot_name)
}


ggplot(agg_users, aes(as.factor(is_churn), y = agg_users$days_played)) +
    geom_boxplot()
ggplot(agg_users, aes(as.factor(is_churn), y = agg_users$num_25)) +
    geom_boxplot()
ggplot(agg_users, aes(as.factor(is_churn), y = agg_users$num_50)) +
    geom_boxplot()
ggplot(agg_users, aes(as.factor(is_churn), y = agg_users$num_75)) +
    geom_boxplot()
ggplot(agg_users, aes(as.factor(is_churn), y = agg_users$num_985)) +
    geom_boxplot()
ggplot(agg_users, aes(as.factor(is_churn), y = agg_users$num_100)) +
    geom_boxplot()
ggplot(agg_users, aes(as.factor(is_churn), y = agg_users$num_unq)) +
    geom_boxplot()
ggplot(agg_users, aes(as.factor(is_churn), y = agg_users$total_secs)) +
    geom_boxplot()
ggplot(agg_users, aes(as.factor(is_churn), y = agg_users$is_churn)) +
    geom_boxplot()
ggplot(agg_users, aes(as.factor(is_churn), y = agg_users$total_skips)) +
    geom_boxplot()
ggplot(agg_users, aes(as.factor(is_churn), y = agg_users$avg_skip_time)) +
    geom_boxplot()
ggplot(agg_users, aes(as.factor(is_churn), y = agg_users$early_skips)) +
    geom_boxplot()
ggplot(agg_users, aes(as.factor(is_churn), y = agg_users$late_skips)) +
    geom_boxplot()
ggplot(agg_users, aes(as.factor(is_churn), y = agg_users$percent_early_skips)) +
    geom_boxplot()
ggplot(agg_users, aes(as.factor(is_churn), y = agg_users$skips_per_secs)) +
    geom_boxplot()
ggplot(agg_users, aes(as.factor(is_churn), y = agg_users$range_proxy)) +
    geom_boxplot()
ggplot(agg_users, aes(as.factor(is_churn), y = agg_users$serach_proxy)) +
    geom_boxplot()
ggplot(agg_users, aes(as.factor(is_churn), y = agg_users$tilt_proxy)) +
    geom_boxplot()
ggplot(agg_users, aes(as.factor(is_churn), y = agg_users$plays_per_unique)) +
    geom_boxplot()
ggplot(agg_users, aes(as.factor(is_churn), y = agg_users$skips_per_full)) +
    geom_boxplot()
ggplot(agg_users, aes(as.factor(is_churn), y = agg_users$outer_skips)) +
    geom_boxplot()
```

Finished plots and data
#### finished plots and data
```{r}
agg_users %>% 
  mutate(is_churn = recode(is_churn, '0'="Retained","1"="Lost")) %>% 
  ggplot(., aes(x=days_played, group = is_churn,fill = is_churn)) +
  geom_histogram(position = "fill") +
  ylab("Percent Churn Decision") +
  xlab("Number of Days With Sessions") +
  ggtitle("Percentage churn", )

#things that correlate with days played:
# -0.2 percent early skips
# -0.2 skips per full
# -0.1 is churn
# 0.2 avg_skip_time
# -0.2 range proxy (unique / early skip)

correl <- round(cor(select(agg_users, -msno)),1)

ggcorrplot(correl, hc.order = T,
           type = "full",
           lab = T,
           lab_size = 2,
           method="square",
           ggtheme = theme_bw)



#percent early skips and total seconds are inversely correlated
#test longer accounts versus listening behavior

```

#### 30 day flag plot 
```{r}
save_df <- T_and_M

plan_df <- T_and_M %>% 
  filter(., payment_plan_days != is.na(payment_plan_days)) %>% 
  mutate(., day30_flag = ifelse(payment_plan_days == 30, "30 Day Plan", "Non-30 Day Plan"))

user_plan <- plan_df %>% 
  ggplot(., aes(x= day30_flag, fill = day30_flag)) +
  geom_bar(stat = "count") +
  ylab("Number of Users in Dataset") +
  xlab("Type of Payment Plan") +
  ggtitle("Users by Plan type") +
  theme(plot.title = element_text(hjust = 0.5))


auto_renew_plot <- plan_df %>% 
  mutate(., is_auto_renew = recode(is_auto_renew, `1`="Auto Renewal", `0`="No Auto Renewal")) %>% 
  ggplot(., aes(x = is_auto_renew, fill = is_auto_renew)) +
  geom_bar() +
  labs(title = "Number of Users by Auto Renewal" ,
       x = "Payment Option",
       y = "Number of Users in Dataset") +
  theme(plot.title = element_text(hjust = 0.5))

selected_plot <- 

plan_df %>% 
  mutate(., is_auto_renew = recode(is_auto_renew, `1`="Auto Renewal", `0`="No Auto Renewal")) %>% 
  ggplot(., aes(x = day30_flag, fill = is_auto_renew, factor = is_auto_renew)) +
  geom_bar() +
  labs(title = "Number of Users by Plan and Renewal" ,
       x = "Plan Option",
       y = "Number of Users in Dataset") +
  theme(plot.title = element_text(hjust = 0.5))


user_plan
auto_renew_plot
selected_plot
ggsave("users by plan length and auto renew", plot = selected_plot, device = "png")
```
```{r}
plan_price_diff <- plan_df %>%
  filter(., is_auto_renew == 1 & day30_flag == "30 Day Plan") %>% 
  group_by(., plan_list_price) %>% 
  summarise(., count = n(), percentage = count / sum(count)) %>% 
  ungroup(.) %>% 
  mutate(.,percentage = (count / sum(count))*100) %>% 
  mutate(., plan_list_price = paste0("$",as.factor(plan_list_price))) %>%
  mutate(., plan_list_price = factor(plan_list_price, levels = c("$99","$100","$119","$120","$129", "$131","$149", "$180"))) %>% 
  ggplot(., aes(x=as.factor(plan_list_price), y = percentage, fill = plan_list_price)) +
  geom_bar(stat = "identity" ) +
  labs(title = "Percentage of Users by Price for 30-day Plan",
       x = "Prices Paid for 30-day Plan",
       y = "Percentage Users of 30-day Plans") +
  theme(plot.title = element_text(hjust = 0.5))

ggsave("plan price diff", plot = plan_price_diff, device = "png")
```

```{r}
plan_df %>%
  filter(., is_auto_renew == 1 & day30_flag == "30 Day Plan") %>% 
  group_by(., plan_list_price, is_churn) %>%
  summarise(., count = n()) %>% 
  mutate(., is_churn = recode(is_churn, '0'="Stayed", '1'="Churn")) %>% 
  spread(., is_churn, count) %>% 
  mutate(., percentage_churn = Churn /(Stayed + Churn))

```

```{r}
#setwd('/Users/jameswelch/Dropbox (Personal)/NYDSA/Work/Hackathons/NYCDSA_Hackathon_Oct_2020/James')
#plans_sita <- read_csv("./plans.csv")

plans_user <- read_csv("by_msno.csv")

#summary(plans_sita)

plans_user %>% 
  ggplot(., aes(x= as.factor(plan_list_price_per_transaction_avg), y =log(num_25_per_session_avg))) +
  geom_boxplot()

plans_sita %>% 
  ggplot(., aes(x= as.factor(plan_list_price), y =num_25_per_session_avg)) +
  geom_bar(stat = "identity")

plans_user %>% 
  ggplot(., aes(x= as.factor(plan_list_price_per_transaction_avg), y =num_50_per_session_avg)) +
  geom_bar(stat = "identity")
plans_user %>% 
  ggplot(., aes(x= as.factor(plan_list_price_per_transaction_avg), y =log(num_50_per_session_avg))) +
  geom_boxplot()


plans_user %>% 
  ggplot(., aes(x= as.factor(plan_list_price), y =num_75_per_session_avg)) +
  geom_bar(stat = "identity")
plans_sita %>% 
  ggplot(., aes(x= as.factor(plan_list_price), y =num_985_per_session_avg)) +
  geom_bar(stat = "identity")
plans_sita %>% 
  ggplot(., aes(x= as.factor(plan_list_price), y =num_100_per_session_avg)) +
  geom_bar(stat = "identity")
plans_sita %>% 
  ggplot(., aes(x= as.factor(plan_list_price), y =num_unq_per_session_avg)) +
  geom_bar(stat = "identity")
plans_sita %>% 
  ggplot(., aes(x= as.factor(plan_list_price), y =total_secs_per_session)) +
  geom_bar(stat = "identity")
#usage seems to increase slightly with higher prices
#make a total interventions / session 

plans_user%>% 
  ggplot(., aes(x= as.factor(plan_list_price_per_transaction_avg), y =age)) +
  geom_boxplot()

#age is nope






plans_user %>% 
  ggplot(., aes(x= as.factor(plan_list_price_per_transaction_avg), y =num_sessions)) +
  geom_violin()
#engagement metric

plans_user %>% 
  ggplot(., aes(x= as.factor(plan_list_price_per_transaction_avg), y =membership_duration)) +
  geom_boxplot()
#mixed

plans_user %>% 
  ggplot(., aes(x= as.factor(plan_list_price_per_transaction_avg), y =log(days_to_expiration))) +
  geom_boxplot()
#eh

plans_user %>% 
  ggplot(., aes(x= as.factor(plan_list_price_per_transaction_avg), y =as.factor(city))) +
  geom_jitter()
#better graph needed

#fuck
plans_user %>% 
  ggplot(., aes(x= as.factor(plan_list_price_per_transaction_avg), y =as.factor(registered_via))) +
  geom_jitter()

plans_user %>% 
  ggplot(., aes(x= as.factor(plan_list_price_per_transaction_avg), y =as.factor(payment_method_id))) +
  geom_jitter()
#doulble fukc



plans_user %>% 
  ggplot(., aes(x= as.factor(plan_list_price_per_transaction_avg), fill =as.factor(is_churn))) +
  geom_bar(position = "fill")
#nope

plans_user %>% 
  ggplot(., aes(x= as.factor(plan_list_price_per_transaction_avg), fill =as.factor(is_female))) +
  geom_bar(position = "fill")

plans_user %>% 
  ggplot(., aes(x= as.factor(plan_list_price_per_transaction_avg), y =as.factor(payment_method_id))) +
  geom_jitter()


plans_user %>% 
  ggplot(., aes(x= as.factor(plan_list_price_per_transaction_avg), fill =as.factor(is_cancel))) +
  geom_bar(position = "fill")


correl <- round(cor(select(plans_user, -msno)),1)

ggcorrplot(correl, hc.order = T,
           type = "full",
           lab = T,
           lab_size = 2,
           method="square",
           ggtheme = theme_bw)

plans_user %>% 
  rowwise() %>% 
  mutate(., total_interventions = sum(num_25_per_session_avg, num_50_per_session_avg, num_75_per_session_avg, num_985_per_session_avg, num_100_per_session_avg)) %>% 
    ggplot(., aes(x= as.factor(plan_list_price_per_transaction_avg), y =log(total_interventions))) +
  geom_boxplot()


```

final graphs
```{r}
#engagement metric
# registred via
# payment method

registration_via_price <- plans_user %>% 
  ggplot(., aes(x= as.factor(plan_list_price_per_transaction_avg), fill =as.factor(registered_via))) +
  geom_bar(position = "fill") +
    scale_fill_brewer(palette = "Set2") +
  labs(title = "Registration Percentage by Plan Cost" ,
       y = "Percentage Registered Via" ,
       x = "Cost of 30-day plan in NT$") +
  theme(plot.title = element_text(hjust = 0.5)) +
  guides(fill=guide_legend(title = "Registration Method"))

#register = age and duration
#payment = neg with list price, and actual paid / memb duration 28% / city

registration_via_price 
ggsave("reg_via_price", plot = registration_via_price , device = "png")


```

```{r}

payment_method_diversity <- plans_user %>% 
  ggplot(., aes(x= as.factor(plan_list_price_per_transaction_avg), y =as.factor(payment_method_id), color = as.factor(is_churn))) +
  geom_jitter() +
  #scale_fill_brewer(palette = "Set2") +
  labs(title = "Diversity of Payment Methods by Plan Cost" ,
       y = "Payment Method Type" ,
       x = "Cost of 30-day plan in NT$") +
  theme(plot.title = element_text(hjust = 0.5)) #+
  #guides(fill=guide_legend(title = "Payment Method"))
payment_method_diversity

ggsave("payment_id_diversity", plot = payment_method_diversity, device = "png")
  
```


```{r}

day30_plans <- plans_user %>% 
  group_by(., plan_list_price_per_transaction_avg) %>%
  summarise(., count= n(), percentage = count / sum(count)) %>% 
  ungroup(.) %>% 
  mutate(.,percentage = (count / sum(count))*100) %>% 
  mutate(., plan_list_price_per_transaction_avg = paste0("$",as.factor(plan_list_price_per_transaction_avg))) %>%
  mutate(., plan_list_price_per_transaction_avg = factor(plan_list_price_per_transaction_avg, levels = c("$99","$100","$129","$149", "$180"))) %>% 
  ggplot(., aes(x=as.factor(plan_list_price_per_transaction_avg), y = percentage, fill = plan_list_price_per_transaction_avg)) +
  geom_bar(stat = "identity" ) +
  labs(title = "Percentage of Users by Price for 30-day Plan",
       x = "Prices Paid for 30-day Plan",
       y = "Percentage Users of 30-day Plans") +
  theme(plot.title = element_text(hjust = 0.5)) +
  guides(fill=guide_legend(title = "Cost of 30-Day Plan"))

ggsave("day30_plans", plot = day30_plans, device = "png")

```


