---
title: "Hackathon Data Analysis"
output: html_notebook
---

Add libraries, import and save files.

```{r}
library(tidyverse)
library(ggplot2)

setwd('/Users/jameswelch/Dropbox (Personal)/NYDSA/Work/Hackathons/NYCDSA_Hackathon_Oct_2020/James')

churn_trunc <- read_csv("./trunc_churn.csv")
members_trunc <- read_csv("./trunc_members.csv")
transaction_trunc <- read_csv("./trunc_transaction.csv")
users_trunc <- read_csv("./trunc_users.csv")
```

Wrange that data
-convert numeric dates to actual date types

```{r, resutls = 'hide'}
# members_trunc <- members_trunc %>% 
#   mutate(.,registration_init_time = as.Date(as.character(registration_init_time),"%Y%m%d"))
# transaction_trunc <- transaction_trunc %>%  
#  mutate(.,transaction_date = as.Date(as.character(transaction_date),"%Y%m%d"))
#transaction_trunc <- transaction_trunc %>%  
#  mutate(.,membership_expire_date = as.Date(as.character(membership_expire_date), format = "%Y %m %d"))
users_trunc <- users_trunc %>%  
  mutate(.,date = as.Date(as.character(date),format = "%Y%m%d"))
```

Churn dataframe for QC
```{r}
print("Churn Dataframe")
print(paste0("total entires: ", length(churn_trunc$is_churn)))
print(paste0("number unique msno: ",length(unique(churn_trunc$msno))))
print(paste0("total churns: ", sum(churn_trunc$is_churn)))
print(paste0("percentage churns: ", sum(churn_trunc$is_churn)/length(churn_trunc$is_churn)*100, "%"))

```
Members dataframe for QC
```{r}
print("Members_trunc")
print(paste0("total entires: ", length(members_trunc$msno)))
print(paste0("number unique msno: ",length(unique(members_trunc$msno))))
print(paste0("number of cities: ", length((unique(members_trunc$city)))))
print(paste0("pop range in each city: ", members_trunc %>% group_by(., city) %>% count() %>%  range() ))
print(paste0("City 1 is probably a null when entering the form, or the first city the company started in."))
members_trunc %>% group_by(., city) %>% count()
print("see grouped_df for by city counts")
hist(members_trunc$city)
print("see histograme for by city counts")
print("see df and histogram for bd")
group_by(members_trunc, as.factor(members_trunc$bd)) %>% count()
hist(members_trunc$bd)
hist(members_trunc[which(members_trunc$bd>=5 & members_trunc$bd<100),]$bd)

print("obvious negaitve and extremely high (>100) can be ignored as truthful. ")
print("age=0 is roughly the same count as city, same member ids?")
print(paste0("gender breakdown(Female/male/NA: ",group_by(members_trunc,gender) %>% count())[2])
print("see datagrame of registration types")
members_trunc %>% group_by(., registered_via) %>% count()
print(paste0("Registration start data range",range(members_trunc$registration_init_time)))

```

Explore usage dataset
assemble dataframe with churn added
```{r}
users_seg <- merge(users_trunc,churn_trunc, by='msno', all = TRUE)
```
```{r}
sum(is.na(users_seg$date))
#head(users_seg,20)
```

How do we characterize a day or activity?
How do we characterize multiple days?
How do we characterize a user?

Ideas
- how does user behavior and likelihood to stay interact?
- city by city usage patterns?
- high intervention versus low intervention in song choice
- are payment methods more likely to churn than others?
- how are the people that leave?
--what does usage look like?
--what payment plans, information?


